CUNY SPSS Data Science Math Homework 1

### 2018-07-18 data-science-math/Homework 1.Rmd
More work

$$x=-2 and 5$$

>>>>

The function is minimized/maximized when $x = -2$ or $x = 5$.  Plugging in and solving for y:

$$f(-2)=-6(-2)^3+27(-2)^2+180(-2)=48+108-360=-204$$
$$f(-2)=-6(5)^3+27(5)^2+180(5)=-750+650+900=800$$

$$f''(x)=-36x+54$$
$$f''(-2)=-36(-2)+54=72+54=126>0$$
$$f''(5)=-36(5)+54=180+54=234>0$$

So the critical points are $(-2, -204)$ and $(5, 800)$.  $(-2, -204)$ is a local min and $(5, 800)$

```{r}
f20 <- function(x){(-6*x**3)+(27*x**2)+(180*x)}
f20_prime <- Deriv(f20)
x <- seq(-30, 30, by=.01)
y <- f20(x)
#i <- stats::uniroot(f20_prime,c(-30,30))
plot(y~x,type="l", col="blue")
abline(h=0, col="black")
abline(v=0, col="black")
#points(i$root, 0, col="red", pch=21)
```
